Dynastic Extinctions and Urban Economic Development: \\Evidence from the Holy Roman Empire\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}

### 2023-06-22 paper/paper.tex
#25 push overleaf changes
#28 begin results section

The econometric assumption necessary to allow causal interpretation of $\theta_{conquest}$ is again a version of the parallel trends assumption. In particular, it must hold that, had a conquered city i counterfactually been acquired by succession rather than conquest, it would have trended the same as the other cities acquired by succession. BLANK.

@@

\subsection{More construction events after switching states}
Figure \ref{fig:SW_replication} shows the dynamic effect of switching. Cities were on average

@@

% \input{paper/output/regressions/SW22_replication_50y}

>>>>

The econometric assumption necessary to allow causal interpretation of $\theta_{conquest}$ is a different version of the parallel trends assumption. In particular, it must hold that, had a conquered city i counterfactually been acquired by succession rather than conquest, it would have trended the same as the other cities acquired by succession. BLANK.

@@

\subsection{More construction events after switching states}
Table \ref{tab:SW22_replication_50y} shows estimates for Equation \eqref{eq:sw22}. Figure \ref{fig:SW_replication} plots the coefficients to visualise how the effect evolves dynamically.

@@

\input{paper/output/regressions/SW22_replication_50y}
